### 2015-05-29 ISWAG_PRESENTATION/PRESENTATION_ISWAG.TEX
iswag pres

%\eadsccr
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\small{

@@

\slidecontents
\renewcommand\theslideheading{Plan}
\slideheading{Introduction}
\textbf{\textcolor{blue}{\large Objective : give you an overview of the meshing optimization done at Cdiscount, the first french e-commerce web site }}
\small{
\newline $\bullet$ Heuristic based optimization algorithm to push specific products 
\newline $\bullet$ An e-commerce pitch
\newline $\bullet$ Semantic similarity and constraining for shrinking our universe
\newline $\bullet$ Big data implementation
\slideheading{Some notations}
Let $N\in\mathbb{N}$ be the number of nodes in our mesh.
Let $\left(X_i\right)_{i \in \left\{1,...,N\right\}}$ be the vertices (URLs) of our oriented graph.
Let $\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}$ be the adjacency matrix of our oriented graph.
Let here define f, a given data per URL, which gives a potentiality metrics for our vertices.
\begin{array}{ccccc}
f & : & \left(X_i\right)_{i \in \left\{1,...,N\right\}} & \to & \mathbb{R}^{+} \\
& & x & \mapsto & f(x) \\
\end{array}
\slideheading{In-rank computation}
We restrain the universe to our site where we compute the standard page-rank.
Initialization :
\forall u \ PR\left(u\right)=\frac{1}{N}
Iterative computation :
PR\left(u\right)= \frac{\left(1-c\right)}{N} + c \times \sum_{v \rightarrow u}\frac{PR\left(v\right)}{card\left(\left\{v\rightarrow u\right\}\right)}
\slideheading{Exhaustive brute force doesn't work}

@@

\slideheading{Picturing our smallest store : jewelery }

@@

\slideheading{Heuristic based algorithm}
We want here to optimize the adequation of our mesh $\left(X_i\right)$ to our potentiality vector $f$.
\max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}}\left\{ \sum^{N}_{i=1} trafic\left(X_i\right)\times pageRank(X_i)\right\}
\slideheading{Genetic algorithm}
\textbf{\textcolor{blue}{\large What a genetic algorithm }}
\small{

@@

\newline \textbf{\textcolor{blue}{\large Why a genetic algorithm }}
\small{

@@

>>>>

	  }
	  %\eadsccr
	  \end{center}
	  \end{slide}
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	  {\small{
	  \begin{slide}
	  \slidecontents
	  \renewcommand\theslideheading{Plan}
	  \end{slide}
	  \begin{slide}
	  \slideheading{Introduction}
	  \textbf{\textcolor{blue}{\large Objective : give you an overview of the meshing optimization done at Cdiscount, the first french e-commerce web site }}
	  \small{
	  \newline $\bullet$ Heuristic based optimization algorithm to push specific products 
	  \newline $\bullet$ An e-commerce pitch
	  \newline $\bullet$ Semantic similarity and constraining for shrinking our universe
	  \newline $\bullet$ Big data implementation
	  }
	  \end{slide}
	  \begin{slide}
	  \slideheading{Heuristic}
	  \textbf{\textcolor{blue}{\large Some notations}}\newline
	  Let $N\in\mathbb{N}$ be the number of nodes in our mesh.
	  \newline
	  Let $\left(X_i\right)_{i \in \left\{1,...,N\right\}}$ be the vertices (URLs) of our oriented graph.
	  \newline
	  Let $\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}$ be the adjacency matrix of our oriented graph.
	  \newline
	  Let here define f, a given data per URL, which gives a potentiality metrics for our vertices.
	  \begin{equation}
	  \begin{array}{ccccc}
	  f & : & \left(X_i\right)_{i \in \left\{1,...,N\right\}} & \to & \mathbb{R}^{+} \\
	  & & x & \mapsto & f(x) \\
	  \end{array}
	  \end{equation}
	  \end{slide}
	  \begin{slide}
	  \textbf{\textcolor{blue}{\large In-rank}}\newline      
	  We restrain the universe to our site where we compute the standard page-rank.
	  \newline
	  Initialization :
	  \begin{equation}
	  \forall u \ PR\left(u\right)=\frac{1}{N}
	  \end{equation} 
	  Iterative computation :
	  \begin{equation}
	  PR\left(u\right)= \frac{\left(1-c\right)}{N} + c \times \sum_{v \rightarrow u}\frac{PR\left(v\right)}{card\left(\left\{v\rightarrow u\right\}\right)}
	  \end{equation}
	  \end{slide}
	  \begin{slide}
	  \textbf{\textcolor{blue}{\large Our heuristic}}\newline 
	  We want here to optimize the adequacy of our mesh $\left(X_i\right)$ to our potentiality vector $f$.
	  We here postulate the following heuristic to assess the relevance of a mesh :
	  \begin{equation}
	  \max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}}\left\{ \sum^{N}_{i=1} trafic\left(X_i\right)\times pageRank(X_i)\right\}
	  \end{equation} 
	  \end{slide}

@@

	  \slideheading{Metaheuristics}    
	  \textbf{\textcolor{blue}{\large Exhaustive brute force doesn't work}}\newline

@@

	  \textbf{\textcolor{blue}{\large Picturing our smallest store : jewelery}}\newline  

@@

	  \textbf{\textcolor{blue}{\large Metaheuristics}}\newline
	  We here have to maximize over all possible graphs. 
	  We have to find a clever global optimization methodology : metaheuristics such as global search, multistart, particle swarm, simulated annealing or genetic algorithm are all good candidates.
	  \textbf{\textcolor{black}{\large What a genetic algorithm}}

@@

	  \newline \textbf{\textcolor{black}{\large Why a genetic algorithm}}

@@

	  \textbf{\textcolor{blue}{\large Cleverly evolving through our universe}}\newline
	    \textbf{\large Child spawning from 2 parents crossover}
	    \epsfig{file=crossover.eps,height=2cm,width=4cm}
	    \textbf{\large Mutation of an individual}
	    \epsfig{file=mutation.eps,height=0.4cm,width=4cm}
	  \slideheading{Shrinking our universe with siloing and semantic similarity}
	    \textbf{\textcolor{blue}{\large Siloing and links categorizing}}\newline
	    \epsfig{file=website_siloing.eps,height=4cm,width=6cm}
	    \epsfig{file=links_categorization.eps,height=1cm,width=6cm}
	    \textbf{\textcolor{blue}{\large Semantic similarity}}\newline
	  We slack our universe by allowing links only between semantically similar URLs :
	  \max_{\left(G_{ij}\right)  \in \left\{0,1\right\}^{N\times N}\ G_{ij}=0 \ if \ CS(ij)\leq t}\left\{ \sum^{N}_{i=1} f\left(X_i\right)\times PR(X_i)\right\}
	  where $CS(ij)$ is a semantic distance between the two linked pages $i$ and $j$.
	  \newline $CS(ij)$ can be defined very easily as the scalar product of the tf/idf vectors of the
	  product descriptions whose weight are defined by the well known formula :
	  w_{ik}=\frac{tf_{ik}\log\left( \frac{N}{n_k}\right)}{\sqrt{\sum_{k=1}^t}(tf_{ik})^2 \log\left(\frac{N}{n_k}\right)^2}
	  \slideheading{Same problem with an e-commerce flavor}
	\sum_{i\in Keywords} SV\left( i\right)\times CTR\left(position\left(i\right)\right)\times CR\left(i\right)\times P\left(i\right)
	where $position\left(i\right)$ is the estimated position in search engine results coming from the modification of our new mesh,
	\\\newline
	$SV\left(i\right)$ is the search volume for the keywords $i$ estimated by the search engine.
	\\\newline
	and $CTR\left(i\right)$ is the click through rate for an URL at the position place in the search engine results.
	\\\newline
	  \slideheading{Prototyping example}
	    $$
    \left(X_i\right)=\{'home','metalist1','metalist2',
    $$
    $$
    'list1','list2','list3','list4',
    $$
    $$
    'product1','product2',...,'product32'\};
    $$
    $$
    f\left(X_i\right) = [100;80;55;$$
    $$
    40;35;25;20;
    $$
    $$
    4;5;...;3]
    $$
    \textbf{\large Initial population}
    \epsfig{file=initial_population.eps,height=5cm,width=5cm}
    \textbf{\large Population at convergence}
    \epsfig{file=converged_population.eps,height=5cm,width=5cm}
    \textbf{\large Best chromosome fitness function evolution}
    \epsfig{file=best_element_evolution.eps,height=5cm,width=5cm}
    The structure found is as we expected arborescent : home linking to metalists, metalists linking to lists and lists to products.
    \textbf{\large Optimal site structure}
    \epsfig{file=site_structure.eps,height=5cm,width=5cm}
	    \slideheading{Big data implementation : Neo4j and Spark GraphX}
	    \epsfig{file=neo4j_maze_runner.eps,height=3cm,width=8cm}
